Distributed Real-time Trajectory Replanning for Robust Motion Execution

### 2018-05-16 paper/paper.tex
paper draft1

\usepackage{graphicx}

@@

\begin{document}
\mainmatter              % start of a contribution
%
% Robust Motion Execution
% 
\title{Distributed Realtime Trajectory Replanning for Robust Motion Execution in Multi-Robot Systems}

%
\titlerunning{Distributed Realtime Trajectory Replanning}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Baskin Senbaslar \and Wolfgang H\"onig \and
Nora Ayanian}
%
%\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Baskin Senbaslar, Wolfgang H\"onig, Nora Ayanian}
%
\institute{University of Southern California, Los Angeles CA, USA,\\
\email{\{baskin.senbaslar, whoenig, ayanian\}@usc.edu}}

@@

\begin{abstract}
\keywords{trajectory planning, collision avoidance, multi-robot systems}
\end{abstract}

@@

We propose robust motion execution as a framework that take pre-planned trajectories as input and compensate for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, or robots breaking down.
Consider the example in Fig.~\ref{fig:swap2:initial}, where two robots are tasked with swapping their position.
The pre-planned trajectories are collision-free, but neither consider a new obstacle nor that the blue robot does not start it the right location.
Robust motion execution can be used to still successfully swap positions, while staying as close as possible to to the pre-planned trajectories (see Fig.~\ref{fig:swap2:final}).
Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and obstacles around them.

\begin{figure}
\centering
\subfloat[Initial configuration.]{
\includegraphics[width=0.48\textwidth]{images/swap2_initial.pdf}
\label{fig:swap2:initial}
}
\hfill
\subfloat[Final configuration and executed trajectories.]{
\includegraphics[width=0.48\textwidth]{images/swap2_final.pdf}
\label{fig:swap2:final}
}
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_initial.pdf}
%\caption{Initial configuration.}
%\label{fig:swap2:initial}
%\end{subfigure} \hfill
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_final.pdf}
%\caption{Final configuration and executed trajectories.}
%\label{fig:swap2:final}
%\end{subfigure}
\caption{Two robots (green and blue circles) are tasked with following their preplanned trajectories (green and blue dashed lines).
The initial plans were created without knowledge of the obstacle (gray) and the blue robot does not start at its planned start position.
Our approach computes smooth trajectories in real-time, avoiding the new obstacle and other robots while staying close to the preplanned trajectory.
}
\label{fig:swap2}
\end{figure}

Robust motion execution is an extension of cooperative collision avoidance where our objective is to stay close to the originally planned trajectories as much as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (see Section~\ref{sec:relatedWork}).
Our method is based on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning with dynamic receding horizon.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.

\todo{perhaps write some more about what experiments we did, after we have the material}

@@

We consider a group of $m$ robots and each robot $i$ is given the following:
\begin{align*}
    \vo_i(t)&:\text{ original trajectory of $i^{th}$ robot where } t\in[0,T_i],\\
    %ct&:\text{ current global time},\\
    %\delta t&:\text{ replanning period},\\
    %\tau&: \text{time horizon},\\ 
    c&:\text{ derivative up to which smoothness is required},\\
    %\cO&:\text{ free space representation of the environment},\\
    %\{\vp_i\}&:\text{ set of positions of all robots},\\
    R_i(\vp)&:\text{ physical extend of robot $i$ at position $\vp$}, and\\
    \gamma_j&: \text{ dynamic limit of robots for $j^{th}$ derivation degree}.%\\
    %&\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
\end{align*}

At time $t$ each robot $i$ can sense the positions $\{\vp_1(t),\ldots,\vp_m(t)\}$ of its neighbors as well as the current occupied space $\cO(t)$ around it.
However, robots cannot communicate with each other and are unaware of the other robots' trajectories.
%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
Each robot $i$ needs to execute a trajectory $\vf_i(t)$ such that:
\begin{align*}
    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
    \text{subject to }& \\
    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i(0)}{dt^j}\text{ for } j\in\{0,1,...,c\}\\
    &\vf_i(t)\text{ is collision free, and}\\ 
    &\left\|\frac{d^j \vf_i(t)}{dt^j}\right\| \leq \gamma_j,\\
    \text{where } & t\in [0,T_i].
\end{align*}

@@

@@

The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ that is bounded by hyperplane $H_i^j$ that separates point $\vp_i$ from $\vp_j$ with normal $\valpha_i^j$ and distance along normal $\beta_i^j$ where $\valpha_i^j\in \R^n$ and $\beta_i^j\in \R$ such that
\begin{align}
    \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\label{voronoiAlpha}\\
    \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i. \label{voronoiBeta}
\end{align}

The set of all buffered voronoi cells is called the buffered voronoi decomposition of the space. For a given buffered voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside one of the buffered voronoi cells at most. We are using this fact in order to guarantee robot-to-robot collision avoidance.

The hyperspace $\cS_i^j$ has the following definition:
\begin{align}
    \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}
\end{align}

Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
\begin{align}
    \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \label{voronoiEquation}.
\end{align}

@@

\subsection{B\'ezier Curves} \label{bezierCurves}
A degree $d$ B\'ezier curve $\vf(t)$ parametrized by duration $T$ is defined by $d+1$ control points $\vP_0, \vP_1, ..., \vP_d \in \R^n$ such that
\begin{align}
    \vf(t; T) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T
\end{align}

The curve starts at $\vP_0$ and ends at $\vP_d$. It does not interpolate the control points, but uses them to guide the curve. A B\'ezier curve lies completely inside the convex hull of its control points \cite{Bernstein}. This is called the \emph{convex hull property of B\'ezier curves}. We use this property to give robot-to-robot and robot-to-obstacle no-collision guarantees.

We use splines as trajectories where each piece is a B\'ezier curve. Given a trajectory $\vf^{K}_i(t)$ for robot $i$ at time step $K$ with $l$ pieces and duration $T^{K}_i$, $T^{K}_{i,j}$ denotes the duration of $j^{th}$ piece, $\vf^{K}_{i,j}(t; T^{K}_{i,j})$ denotes the $j^{th}$ piece of the trajectory, $\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of $j^{th}$ piece, and $P^{K}_{i,j,\rho}[u]$ denotes the $u^{th}$ coordinate of that control point where $j \in \{1,2,...,l\}$, $\rho \in \{0,1,...,d\}$, and $u \in \{1,2,...,n\}$.

\subsection{Support Vector Machine}\label{svmSection}
A support vector machine is a supervised learning method that is used to classify data into several classes.
In binary classification problems, we are given a linearly separable data set $\{(\vx_i, y_i)\}$ where $\vx_i \in \R^n$ is a data point and $y_i \in \{-1, 1\}$ is the corresponding class label.
The goal is to find a hyperplane with normal $\vw$ and distance along the normal $\frac{b}{\|w\|}$ that separates the two classes.
The SVM problem for binary classification with a separable data set can be stated as the following quadratic optimization problem with hard constraints \cite{SVM}:
\begin{align*}
    \text{minimize}\ \ \  &\|\vw\|\\
    \text{subject to}\ \ \  & y_i(\vw \cdot \vx_i - b) \geq 1
\end{align*}
We use SVMs to define collision free convex subspaces that are obstacle-free.
\subsection{Trajectory Optimization} \label{trajectoryOptimization}
A part of our replanning approach utilizes quadratic programming for trajectory optimization using control points of curves as decision variables. The overall structure of our quadratic optimization problem is as follows:
\begin{align*}
    \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^T\vg\\
    \text{subject to}\ \ \ & \vlbA \leq A\vx \leq \vubA
    % &\vlb \leq \vx \leq \vub
\end{align*}
%, while bounds on variables are represented with vectors the $\vlb$ and the $\vub$.

@@

There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.

\begin{description}
\item [Initial Point Constraints]
An initial point constraint on a B\'ezier curve requires the first control point of the curve to be equal to a given vector. This requires $n$ linear constraints on the control points, $n$ being the dimension we are working in.

\item[Continuity Constraints]
A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ in the end to be equal to the curve $j+1$ in the beginning in any order of derivation. We take the vector difference of those values and require it to be equal to $\vzero$. This requires $n$ linear constraints on the control points.

\item[Hyperspace Constraints]
A hyperspace constraint requires a point of a curve to be on a specific side of a hyperplane. Given a hyperplane with normal $\vn$ and distance along the normal $b$, the hyperspace constraint requires $1$ linear constraint on the control points.
\end{description}

@@

\subsection{Approach Overview}
Our approach has three major components: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot.

In each iteration $K$, each robot executes the flow chart outlined in Fig. ~\ref{fig:flowchart}. Replanning is done at a fixed period of $\delta t$ and results in a trajectory $f^K_i(t)$ that is defined for $t\in [0,\tau]$, safe to execute up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.

In the beginning of each iteration, we check several conditions to decide if discrete planning is required. If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth. We use this discrete path as an initial guess in trajectory optimization. If discrete planning is not required, we skip discrete search, and directly use the control points of the previous plan as the initial variables.

Depending on whether discrete search is done or not, we construct the objective matrix $H$ and objective vector $g$ for trajectory optimization in a slightly different way. Exact difference in construction processes is explained in ~\ref{continuousOptimization}.

Than, we compute the $A$ matrix that represents continuity, hyperspace, and initial point constraints. Robot-to-robot collision avoidance is enforced with buffered voronoi decomposition of the space while robot-to-obstacle collision avoidance is enforced with SVM hyperspaces that we calculate between trajectory pieces and the obstacles. Since quadratic optimization requires constraints to be linear and dynamic limits can't be represented as linear constraints, we check dynamic limit violations not during trajectory optimization but in the temporal rescaling stage that runs after optimization. As long as dynamic limits are violated, we increase durations of pieces and do the optimization again until dynamic limits are not violated. In the end, we have a trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is $C^{(c)}$ continuous, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.

\begin{figure}
%\begin{adjustbox}{width=\textwidth,caption={bla}}
\resizebox{\textwidth}{!}{
% \footnotesize
\begin{tikzpicture}[node distance = 2cm]
    \node (discrete) [decision, text width=2cm] {need discrete replanning?};
    \node (discretesearch) [process, right of=discrete, xshift=1.2cm, yshift = 1cm, text width = 2cm] {discrete search};
    \node (discobjbuild) [process, right of=discretesearch, xshift = 1cm, text width = 2cm] {discrete objective builder};
    \node (contobjbuild) [process, below of=discobjbuild, text width = 2cm] {continuous objective builder};
    \node (constraintbuild) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width=2cm]
    {constraint builder};
    \node (trajopt) [process, right of=constraintbuild, xshift = 1cm, text width = 2cm] {trajectory optimization};
    \node (dynamiclimits) [decision, right of=trajopt, xshift = 1.5cm, text width = 2cm] {dynamic limits violated?};
    \node (rescale) [process, below of = dynamiclimits, text width = 2cm, yshift = -0.75cm] {rescaling};
    %\node (end) [io, right of = dynamiclimits, text width = 2cm, xshift = 2.5cm] {use trajectory for $\delta t$};

@@

    \draw [arrow] (discrete) -- node[anchor=south] {yes} (discretesearch);
    \draw [arrow] (discrete) -- node[anchor=north] {no} (contobjbuild);
    \draw [arrow] (discretesearch) -- (discobjbuild);
    \draw [arrow] (discobjbuild) -- (constraintbuild);
    \draw [arrow] (contobjbuild) -- (constraintbuild);
    \draw [arrow] (constraintbuild) -- (trajopt);
    \draw [arrow] (trajopt) -- (dynamiclimits);
    \draw [arrow] (dynamiclimits) -- ++(2.5,0) node[anchor=south] {no} -- ++(0,-4) --  ++(-5,0) -- ++(-4,0) node[anchor=south] {start next iteration} -|   (discrete);
    \draw [arrow] (dynamiclimits) -- node[anchor=east] {yes} (rescale);
    \draw [arrow] (rescale) -| (trajopt);

    \node[right = 0cm of c1, yshift=0.3cm] {Discrete planning};
    \node[right = 0cm of c5, yshift=0.3cm] {Continuous optimization};
    \node[right = 0cm of c9, yshift=0.3cm] {Temporal rescaling};

@@

We execute discrete planning if any of the following conditions is true:
\begin{enumerate}
    \item The original trajectory is not collision-free for the time horizon, i.e., $\exists t\in [\psi,\psi+\tau] : R_i(\vo_i(\psi)) \cap \cO(\psi) \neq \emptyset$,
    \item The first piece of the planned trajectory is outside robot $i$'s buffered voronoi cell, i.e., $\exists t\in [0, T^{K}_{i,1}] : \vf^{K}_{i,1}(t; T^{K}_{i,1}) \not\in \cV_i(\psi)$, or
    \item The planned trajectory is not collision-free for the time horizon, i.e., $\exists t\in [0,\tau] :  R_i(\vf^{K}_i(t)) \cap \cO(\psi) \neq \emptyset$.
\end{enumerate}
The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second case handles cases where previously unknown robots appear, and the third condition handles dynamic obstacles.

>>>>

\usepackage{graphicx}
%\usepackage{nicefrac}

@@

\begin{document}
\mainmatter              % start of a contribution
%
% Robust Motion Execution
% 
\title{Distributed Real-time Trajectory Replanning for Robust Motion Execution}% in Multi-Robot Systems}

%
%\titlerunning{Distributed Real-time Trajectory Replanning}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Baskin Senbaslar \and Wolfgang H\"onig \and
Nora Ayanian}
%
%\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Baskin Senbaslar, Wolfgang H\"onig, Nora Ayanian}
%
\institute{University of Southern California, Los Angeles CA, USA,\\
\email{\{baskin.senbaslar, whoenig, ayanian\}@usc.edu}}

@@

\begin{abstract}
We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution, newly appearing obstacles, or robots breaking down.
Robots do not communicate with each other and only need to be able to sense the other robots' positions and the obstacles.
At the low-level, we use buffered voronoi cells as multi-robot collision avoidance strategy.
At the high-level we use a hybrid planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
The discrete planner helps to avoid local minima effectively, adjusts the planning horizon, and provides good initial guesses for the optimization stage.
Trajectory optimization uses a quadratic programming formulation, where all safety-critical parts are formulated as hard constraints.
We demonstrate our approach in simulation and on real robots, showcasing that it can operate in real-time.
%\keywords{trajectory planning, collision avoidance, multi-robot systems}
\end{abstract}

@@

We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, or robots breaking down.
Consider the example in Fig.~\ref{fig:swap2}, where two robots are tasked with swapping their position.
The pre-planned trajectories are collision-free, but neither consider a new obstacle nor that the blue robot does not start it the correct location.
Robust motion execution can be used to still successfully swap positions, while staying as close as possible to to the pre-planned trajectories.
Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and obstacles around them.

\begin{figure}
%\centering
%\subfloat[Initial configuration and pre-planned trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_initial.pdf}
%\label{fig:swap2:initial}
%}
\hfill
%\subfloat[Final configuration and executed trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_final.pdf}
%\label{fig:swap2:final}
%}
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_initial.pdf}
%\caption{Initial configuration.}
%\label{fig:swap2:initial}
%\end{subfigure} \hfill
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_final.pdf}
%\caption{Final configuration and executed trajectories.}
%\label{fig:swap2:final}
%\end{subfigure}
\caption{Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines; (a)).
The initial plans were created without knowledge of the obstacle (gray) and the blue robot does not start at its planned start position.
Our approach computes smooth trajectories in real-time, avoiding the new obstacle and other robots while staying close to the pre-planned trajectory (b).
}
\label{fig:swap2}
\end{figure}

Robust motion execution is an extension of cooperative collision avoidance where the objective is to stay close to the originally planned trajectories as much as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (see Section~\ref{sec:relatedWork}).
Our method is based on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning with dynamic receding horizon.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.

%\todo{perhaps write some more about what experiments we did, after we have the material}

@@

We consider a group of $m$ robots and each robot $i$ is given the following:
\begin{align*}
    \vo_i(t)&:\text{ original trajectory of $i^{th}$ robot where } t\in[0,T_i],\\
    %ct&:\text{ current global time},\\
    %\delta t&:\text{ replanning period},\\
    %\tau&: \text{time horizon},\\ 
    c&:\text{ derivative up to which smoothness is required},\\
    %\cO&:\text{ free space representation of the environment},\\
    %\{\vp_i\}&:\text{ set of positions of all robots},\\
    R_i(\vp)&:\text{ physical extent of robot $i$ at position $\vp$, and}\\
    \gamma_j&: \text{ dynamic limit of robots for $j^{th}$ derivation degree}.%\\
    %&\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
\end{align*}

At time $t$, each robot $i$ can sense the positions $\{\vp_1(t),\ldots,\vp_m(t)\}$ of its neighbors as well as the current occupied space $\cO(t)$ around it.
We assume that $\cO(t)$ is a set of $\uptheta$ convex obstacles, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap}.
However, robots cannot communicate with each other and are unaware of the other robots' trajectories.
%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
Each robot $i$ needs to execute a trajectory $\vf_i(t)$ such that:
\begin{align}
\begin{split}
    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
    \text{subject to }& \\
    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i(0)}{dt^j}\text{ for } j\in\{0,1,...,c\}\\
    &\vf_i(t)\text{ is collision free, and}\\ 
    &\left\|\frac{d^j \vf_i(t)}{dt^j}\right\| \leq \gamma_j,\\
    \text{where } & t\in [0,T_i].
\end{split}
\label{eq:problem:opt}
\end{align}

@@

We now introduce important mathematical concepts and notation.

@@

The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ that is bounded by hyperplane $H_i^j$ that separates point $\vp_i$ from $\vp_j$ with normal $\valpha_i^j$ and distance along normal $\beta_i^j$ where $\valpha_i^j\in \R^n$ and $\beta_i^j\in \R$ such that
\begin{equation}
    \valpha_i^j = \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|} \text{ and }
    \beta_i^j = \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i.
    \label{voronoiAlphaBeta}
\end{equation}
% \begin{align}
%     \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\label{voronoiAlpha}\\
%     \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i. \label{voronoiBeta}
% \end{align}

The set of all buffered voronoi cells is called the buffered voronoi decomposition of the space.
For a given buffered voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside one of the buffered voronoi cells at most.
We use this property in order to avoid robot-to-robot collisions.

Using the hyperspaces $\cS_i^j$ we can reformulate $\cV_i$:
\begin{equation}
    \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \text{ , where } \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}.
    \label{voronoiEquation}
\end{equation}

% \begin{align}
%     \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}
% \end{align}

% Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
% \begin{align}
%     \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \label{voronoiEquation}.
% \end{align}

@@

\subsection{B\'ezier Curves} \label{bezierCurves}
A degree $d$ B\'ezier curve $\vf(t)$ parametrized by duration $T$ is defined by $d+1$ control points $\vP_0, \vP_1, ..., \vP_d \in \R^n$ such that
\begin{align}
    \vf(t; T) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T.
\end{align}

The curve starts at $\vP_0$ and ends at $\vP_d$. It does not interpolate the control points, but uses them to guide the curve.
A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein}.
%This is called the \emph{convex hull property of B\'ezier curves}.
We use this property to avoid robot-to-obstacle collisions.

We use splines as trajectories where each piece is a B\'ezier curve. Given a trajectory $\vf^{K}_i(t)$ for robot $i$ at iteration $K$ with $l$ pieces and duration $T^{K}_i$, $T^{K}_{i,j}$ denotes the duration of the $j^{th}$ piece, $\vf^{K}_{i,j}(t)$ denotes the $j^{th}$ piece of the trajectory, and $\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of the $j^{th}$ piece where $t\in[0, T^{K}_{i,j}]$, $j \in \{1,2,\ldots,l\}$ and $\rho \in \{0,1,\ldots,d\}$.

% \subsection{Support Vector Machine}\label{svmSection}
% A support vector machine is a supervised learning method that is used to classify data into several classes.
% In binary classification problems, we are given a linearly separable data set $\{(\vx_i, y_i)\}$ where $\vx_i \in \R^n$ is a data point and $y_i \in \{-1, 1\}$ is the corresponding class label.
% The goal is to find a hyperplane with normal $\vw$ and distance along the normal $\frac{b}{\|w\|}$ that separates the two classes.
% The SVM problem for binary classification with a separable data set can be stated as the following quadratic optimization problem with hard constraints \cite{SVM}:
% \begin{align*}
%     \text{minimize}\ \ \  &\|\vw\|\\
%     \text{subject to}\ \ \  & y_i(\vw \cdot \vx_i - b) \geq 1
% \end{align*}
% We use SVMs to define collision free convex subspaces that are obstacle-free.

\subsection{Trajectory Optimization using Quadratic Programming} \label{trajectoryOptimization}
A part of our replanning approach utilizes \emph{quadratic programming} (QP) for trajectory optimization.
The decision variables $\vx$ are all B\'ezier curve control points concatenated.
The overall structure of our quadratic optimization problem is as follows:
\begin{align}
\begin{split}
    \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^T\vg\\
    \text{subject to}\ \ \ & \vlbA \leq A\vx \leq \vubA.
    % &\vlb \leq \vx \leq \vub
\end{split}
\end{align}
%, while bounds on variables are represented with vectors the $\vlb$ and the $\vub$.

@@

There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
An initial point constraint on a B\'ezier curve requires the initial point of the curve to be equal to a given vector for a specified derivative.
A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ at the end to be equal to the curve $j+1$ at the beginning in any order of derivation.
We take the vector difference of those values and require it to be equal to $\vzero$.
A hyperspace constraint requires all points of a curve to be on a specific side of a hyperplane.
The construction of the QP is discussed in previous work~\cite{crazyplanning-ieeetro}.

% There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.

% \begin{description}
% \item [Initial Point Constraints]
% An initial point constraint on a B\'ezier curve requires the first control point of the curve to be equal to a given vector.
% This requires $n$ linear constraints on the control points. %, $n$ being the dimension we are working in.

% \item[Continuity Constraints]
% A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ at the end to be equal to the curve $j+1$ at the beginning in any order of derivation.
% We take the vector difference of those values and require it to be equal to $\vzero$.
% This requires $n$ linear constraints on the control points.

% \item[Hyperspace Constraints]
% A hyperspace constraint requires all points of a curve to be on a specific side of a hyperplane.
% Given a hyperplane with normal $\vn$ and distance along the normal $b$, the hyperspace constraint requires one linear constraint for each relevant control point.
% \end{description}

% The construction of the QP is discussed in more detail in previous work~\cite{crazyplanning-ieeetro}.

@@

%\subsection{Approach Overview}
Replanning is done at a fixed period of $\delta t$ and at each iteration $K$ we compute a trajectory $f^K_i(t)$.
The planning horizon $\tau'$ is automatically adjusted, but a user can provide the desired planning horizon $\tau$.
In the following, we assume that the robots are spherical with a uniform radius $r_s$.
%The trajectory $f^K_i(t)$ is safe to execute at least up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.

We execute the following three major components iteratively: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot, see Fig.~\ref{fig:flowchart}.
In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth.
We use this discrete path as an initial guess in trajectory optimization.
If discrete planning is not required, we use the control points of the previous plan as the initial guess.

We construct a QP with hard constraints for trajectory optimization in a slightly different way, depending if discrete planning was executed or not.
In both cases, buffered voronoi cells are used to ensure collision-free operation for up to $\delta t$ and collisions with static obstacles are avoided for the planning horizon.

Dynamic limits cannot be represented as linear constraints in our QP.
Thus, we check dynamic limit violations in the temporal rescaling stage that runs after optimization.
As long as dynamic limits are violated, we increase the durations of all trajectory pieces uniformly, followed by re-solving the QP.

At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c^{th}$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration.

\begin{figure}
\centering
%\begin{adjustbox}{width=\textwidth,caption={bla}}
\resizebox{0.9\textwidth}{!}{
% \footnotesize
\begin{tikzpicture}[node distance = 2cm]
    \node (discrete) [decision, text width=2cm] {Discrete replanning required?};
    \node (discretesearch) [process, right of=discrete, xshift=1.5cm, yshift = 1cm, text width = 2cm] {Discrete Search};
    \node (discobjbuild) [process, right of=discretesearch, xshift = 1cm, text width = 2cm] {Construct QP};
    \node (contobjbuild) [process, below of=discobjbuild, text width = 2cm] {Construct QP};
    %\node (constraintbuild) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width=2cm]
    %{constraint builder};
    \node (trajopt) [process, right of=discobjbuild, yshift = -0.75cm, xshift = 1cm, text width = 2.5cm] {Trajectory Optimization};
    \node (dynamiclimits) [decision, right of=trajopt, xshift = 2.0cm, text width = 2cm] {Dynamic limits violated?};
    \node (rescale) [process, below of = dynamiclimits, text width = 2cm, yshift = -0.75cm] {Rescaling};
    %\node (end) [io, right of = dynamiclimits, text width = 2cm, xshift = 2.5cm] {use trajectory for $\delta t$};

@@

    \draw [arrow] (discrete) -- node[anchor=south] {Yes} (discretesearch);
    \draw [arrow] (discrete) -- node[anchor=north] {No} (contobjbuild);
    \draw [arrow] (discretesearch) -- (discobjbuild);
    \draw [arrow] (discobjbuild) -- (trajopt);
    \draw [arrow] (contobjbuild) -- (trajopt);
    %\draw [arrow] (constraintbuild) -- (trajopt);
    \draw [arrow] (trajopt) -- (dynamiclimits);
    \draw [arrow] (dynamiclimits) -- ++(2.5,0) node[anchor=south] {No} -- ++(0,-4) --  ++(-5,0) -- ++(-4,0) node[anchor=south] {Start next iteration} -|   (discrete);
    \draw [arrow] (dynamiclimits) -- node[anchor=east] {Yes} (rescale);
    \draw [arrow] (rescale) -| (trajopt);

    \node[right = 0cm of c1, yshift=0.3cm] {Discrete Planning (\ref{discretePlanning})};
    \node[right = 0cm of c5, yshift=0.3cm] {Continuous Optimization (\ref{continuousOptimization})};
    \node[right = 0cm of c9, yshift=0.3cm] {Temporal Rescaling (\ref{temporalRescaling})};

@@

Robot $i$ executes discrete planning if any of the following conditions is true:
\begin{enumerate}
    \item The original trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [\psi,\psi+\tau] : R_i(\vo_i(t)) \cap \cO(\psi) \neq \emptyset$,
    \item The first piece of the previously planned trajectory is outside the robot's buffered voronoi cell, i.e., $\exists t\in [0, T^{K-1}_{i,1}] : \vf^{K-1}_{i,1}(t) \not\in \cV_i(\psi)$, or
    \item The previously planned trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [0,\tau] :  R_i(\vf^{K-1}_i(t)) \cap \cO(\psi) \neq \emptyset$.
\end{enumerate}
The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second case handles cases where previously unknown robots appear, and the third condition handles numeric issues and dynamic obstacles.

Discrete planning uses a dynamic receding horizon approach. First, we find the earliest time $\tau'\in [\min(\tau, T_i-\psi), T_i-\psi]$ where the original trajectory is collision-free with respect to both obstacles and other robots.
Second, we use a discrete graph search to find a path from the robots current location to $\vo_i(\psi+\tau')$ that avoids both static obstacles and other robots.
If $\tau'$ does not exist or no solution path exists, we skip the discrete planning stage.
Third, we use the first $l$ segments of the discrete path to uniformly place the new estimated control points on top of those segments.
In case the discrete path has fewer than $l$ segments, the last discrete segment is shared between multiple B\'ezier curves.
Finally, we adjust $T_{i,j}^K$ relative to the segment lengths and scale by $\tau'$, such that we would arrive at time $\psi+\tau'$ at location $\vo_i(\psi+\tau')$ if we would follow the discrete path with constant speed.
However, to guarantee collision-free operation, we ensure that $T_{i,1}^K\geq \delta t$ in any case.
